
\documentclass{resume} % Use the custom resume.cls style
\usepackage{xcolor}%定义了一些颜色
\usepackage{colortbl,booktabs}%第二个包定义了几个*rule
\usepackage{hyperref}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{enumerate}
\usepackage{changepage}

\name{Yonggang Jiang} % Your name
\address{Tel: (+86) 181-7088-0522 $\diamond$ E-mail: \href{mailto:yonggangjiang@smail.nju.edu.cn}{yonggangjiang@smail.nju.edu.cn}}
\address{163 Xianlin Avenue, Qixia District, Nanjing, Jiangsu, China 210023}

% \address{Webpage: \url{ http://sunnyszy.me}}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-2pt}
\begin{rSection}{Education}
{\bf Nanjing University} \hfill {\em Sep. 2017 - Jul. 2021(expected)} \\
B.C. in Computer Science and Technology, Elite Program \\
GPA: 94.4/100 {\em (Major)} ~ 92.4/100 {\em (Overall)}\\
Ranking: 1/31 {\em (Major)} ~ 3/204 {\em (Overall)}\smallskip\\
{\bf University of California, Berkeley} \hfill {\em Jan. 2020 - May. 2020} \\
Berkeley International Study Program
\smallskip\\
GPA: 4.0/4.0
\end{rSection}

%\begin{rSection}{Publications}
%$[1]$ X. Tong, {\bf Jiachen Sun}, Xiaohua Tian. ``{\bf FineLoc: A Fine-grained Self-calibrating Wireless Indoor Localization System}'' submitted to {\em Infocom}. 2018.\medskip\\
%$[2]$ {\bf Jiachen Sun}$^\dagger$, Y. Zhang$^\dagger$, Y. Yao$^\dagger$. ``{\bf Replacing the Kariba Dam}'' {\em UMAP Journal of Undergraduate Mathematics and Its Applications}. 2017. $^\dagger$Co-primary Authors
%\end{rSection}
\begin{rSection}{Research Experience}

{\large Research work in TCS group at {\bf Nanjing University} }

\begin{rSubsection}{Contention resolution problem with jamming and without collision detection}{\em Aug. 2020 - Feb. 2021}{ (Advisor: \href{https://chaodong.me/}{\bf Prof. Chaodong Zheng})}{}
\item Provide tight lower bound and upper bound for contention resolution problem with jamming and without collision detection when considering the tradeoff between active slots, number of arrived players, and number of jammed slots. 
\item My contribution in this work: proving all lower bounds, proving some key lemmas in the analysis of the algorithm, contributing to the idea of analyzing algorithm. 
\end{rSubsection}
\end{rSection}

\begin{rSection}{Publications}
*The co-authors of papers are listed in alphabetical order.
\begin{enumerate}[{[}1{] }{ }]
\setlength{\itemindent}{0em}
    \item \href{https://arxiv.org/abs/2102.09716}{\textbf{Tight Trade-off in Contention Resolution without Collision Detection.}}\\
    Haimin Chen, \underline{Yonggang Jiang}, Chaodong Zheng. \\ \emph{In submission.}
\end{enumerate}
\end{rSection}

\begin{rSection}{Teaching Assistant}
\textbf{Data Structures and Algorithms, Nanjing University, Fall 2019,  \href{https://chaodong.me/teaching/dsalg/2020/course-homepage.html}{Fall 2020}}\\
\textbf{Combinatorics, Spring 2021}
\end{rSection}
\begin{rSection}{Honors \& Awards}
National Elite Program Scholarship, Outstanding Prize (top 1)\hfill{\em 2019-2020}\\
National Elite Program Scholarship, Outstanding Prize (top 1)\hfill{\em 2018-2019}\\
National Elite Program Scholarship, First Prize (top 1)\hfill{\em 2017-2018}\\
CCPC Regional Contest, Gold Medal: Guilin \hfill{\em 2018}\\
ACM-ICPC Asia Regional Contest, Silver Medal: Jiaozuo \hfill{\em 2018}\\
NOIP First Prize \hfill{\em 2015}\\
\end{rSection}
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{2ex}} l }
Computer Languages & C/C++, Java, SQL\\
English & TOEFL({\em MyBest™}):
104 (Reading 29, Listening 29, Speaking 23, Writing 23)\\
GRE & 323 (Verbal 153, Quantitative 170, Writing 3.5)
\end{tabular}
\end{rSection}
\end{document}
